### 2012-08-24 inst/examples/unmanaged_warning.Rmd
added summary stats graphs. #21

``` {r earlywarning}
acor_tau <- warningtrend(dat, window_autocorr)
var_tau <- warningtrend(dat, window_var)
````

@@

@@

``` {r parallel}
library(snow)
library(methods)
#cl <- makeCluster(20, type = "MPI")
#clusterEvalQ(cl, library(earlywarning))
#clusterExport(cl, ls())
#clusterExport(cl, list = c("A", "B"))
require(snowfall)
sfInit(par=T, cpu=12)
sfLibrary(earlywarning)
sfExportAll() 
```

>>>>

``` {r earlywarning}
acor_tau <- warningtrend(dat, window_autocorr)
var_tau <- warningtrend(dat, window_var)

acor_tau
var_tau
````

@@

``` {r summarystat_roc} 
summarystat_roc <- function(A,B, summarystat_functions, reps=200){
  require(plyr)
  require(reshape2)
  Asim <- simulate(A, reps)
  Bsim <- simulate(B, reps)
  sim <- melt(Asim, id = "time")
  Bsim <- melt(Bsim, id = "time")
  names(Asim)[2] <- "rep"
  names(Bsim)[2] <- "rep"
	dat <- lapply(summarystat_functions, function(f){
	  wsA <- ddply(Asim, "rep", warningtrend, f)
  	wsB <- ddply(Bsim, "rep", warningtrend, f)
	  data.frame(null = wsA$tau, test = wsB$tau)
	})
	tidy <- melt(dat)
}

tau_dist <- summarystat_roc(A, B, list(var=window_var, acor=window_autocorr))
head(tau_dist)
```

@@

``` {r parallel}
require(snowfall)
sfInit(par=T, cpu=12)
sfLibrary(earlywarning)
sfExportAll() 
```
